---
title: "NGS CMC Seoul"
author: 
  - "Jun Kang"
date: '20210407'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF",
  
)
```

# Primary purpose

- Find drugable genomic alteration
- Let's list up

---
# My workflow

---
## Check whether the variants found is relevant for the cancer type
  - EGFR for lung cancer
  - KRAS, APC for colon cancer
  - If in doubt, look at histological diagnosis and the unusual variants

---
# Look at the variants called
  - Unusual variants (possible false positive)
  - Germline polymorphism
    - Allele frequency
    - ClinVar https://www.ncbi.nlm.nih.gov/clinvar/
  - Allignment error
    - Frameshift variant
    - IGV
  - Splicing site variants
    - VUS
    - ClinVar
  - Low read count fusion
    - Less than 1000 readcount
    - Primer-dimer
    - Other methods IHC, FISH

---
# Check IGV

---
# Check Whitelist

- Check QC
  - Pass is not enough
    - Total mapped RNA read 
    - > 500,000 is not enough
    - MAPD for CNV
- Check filter out variants by sorting

---
# Check BRCA1/2 for breast, ovary, pancreas and prostate

- Filter out variants by sorting
- myBRCAvariant_filter
- https://www.ncbi.nlm.nih.gov/clinvar/
- Evaluate the variants https://www.sciencedirect.com/science/article/pii/S0002929716300349?via%3Dihub

---
# Check annotations

- Examples
  - EGFR Exon20 deletion
  - http://varnomen.hgvs.org/

--- 
# Interpretation
- http://10.10.56.106:3729/

---
# Note edit

--- 
# What to do

- Memo on printed NGS management system
- Fill in interpretation
- TAT is important

