---
title: Tidymodel and glmnet
author: JK
date: '2020-03-18'
slug: tidymodel-and-glmnet
categories:
  - R
  - Stastics
  - Tidymodel
tags:
  - R
  - RStudio
  - Machine learning
  - Demo
subtitle: ''
summary: ''
authors: []
lastmod: '2020-03-18T18:42:03+09:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r, echo=FALSE}
library(knitr)
read_chunk("./scripts/tidymodel_glmn.R")
```

```{r, echo=FALSE}
<<library>>
```

When the penalized generalize linear model (Lasso or Ridge) is processed in the tidymodel environment, finalizing the hyperparameter (lambda) and getting coefficients of the final model are confusing. Here is an example. This example predicts PIK3CA mutation status by gene expression data. TCGA breast cancer dataset is used.  

```{r, echo=FALSE}
<<load>>
```

##### Modeling  
```{r tidymodel}
<<tidymodel>>
```

```{r}
<<workflow>>
```

- Grid parameter search on 10-fold cross-validation with 5 repeats  
- Dummy variable to control for histologic subtype 

##### Select best parameter  
```{r, cache=TRUE}
<<fitting>>
```


##### Finalizing  
```{r finalizing}
<<Finalize_model>>
```

```finalize_workflow()``` finalizes the model with selected optimal hyperparameters. However, the glmnet fits any lambda, not the indicated lambda. This was discussed at https://github.com/tidymodels/parsnip/issues/195. The glmnet is more efficient to fit all lambda than a single lambda. Thus tidymodel ignores the indicated lambda. This made the first confusion. **The finalization can be finalized by predict in tidymodel environment.** Finalize with ```predict```. Note the last argument ```penalty = 1``` of ```stats::predict(wfl_final, type = "prob", new_data = trainset_ahDiff, penalty = 1)```.

```{r predict}
<<trainset_prediction>>
```


##### Performance
```{r performance}
<<performance>>
```

Because glmnet fits the whole path, there are whole coefficients in the glmnet fit object ```wfl_final```. This was the second confusion. How to get the final model coefficients is below.  

##### Coefficients    
```{r coeffi}
<<coefficiency>>
```


