---
title: RStudio Conference 2020
author: JK
date: '2020-01-29'
slug: rstudio-conference-2020
categories:
  - R
tags:
  - R
  - RStudio
  - RStudio conference
  - Shiny
subtitle: ''
summary: ''
authors: []
lastmod: '2020-01-29T17:51:24-08:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: 
draft: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    error = FALSE,
    message = FALSE,
    cache = TRUE
)
```

Key Note

J.J. Allaire

RStudio becomes Public B Corp.

J.J. Allaire's favorite book Fooled by Randomness


```{r echo=FALSE}
blogdown::shortcodes('tweet', c('1222577749824401408',
                                #'1222574431521738752',
                                '1222574214747607042'))
```
---
Google AI PAIR team  
Fernanda Viegas, Martin Wattenberg  

Debug your data first, not your program!  

Visualization, Hello World Image data set has faulty annotations.  
Validate your data set!! 

High dimensionality, MNIST data set PCA clustering.

Fairness, Different views of points can be visualized. People can understand it.

```{r}
blogdown::shortcodes('tweet', c('1222585238473203712',
                                '1222593520508141568',
                                '1222581456829992960'))
```


https://pair.withgoogle.com

---
Development  
Plumber API  

After modeling with R, through an application programming interface (API) the model can be used by other applications. 

Applications using R and Plumber

T-mobile Heather Nolis, Jacqueline Nolis
'We're strictly a java shop'
{loadtest} Rpackage for performance test
---
Andrew Mangan, Salesforce  

Analytics using R

---
James Blair, RStudio  

Practical Plumber Patterns  
Packaging plumber  
A package as a deploying method  



Alex Gold  RStudio  
Develop a public bicycle prediction app  
Shiny, Plumber, and Pin  
The Package Pins helps real-time data IO management.  

Jenny  

Debugging 4 steps  

https://github.com/jennybc/debugging#readme  

```{r}
blogdown::shortcode('tweet', '1222935148691247105')

```
----
Shiny  

Colin Fay, ThinkR  

{Golem}, a framework for production-grade Shiny apps  

---

Mine Cetinkaya-Rundelm, RStudio  

Shiny contest, open codes  
---

Joe Cheng, RStudio  

Styling Shiny with Sass and Bootstrap 4  
Bootstrap 4 is default Shiny frame. Bootstrap 4 supports Sass which is a meta-program for CSS. {bootstraplib} makes easy to use Sass in R environment.  


```{r}
blogdown::shortcodes('tweet',
                     c('1222664917280387072',
                       '1222652894354141184'))
```

```{r}
blogdown::shortcode('tweet', '1222603023605624832')
blogdown::shortcode('tweet', '1222611273021394944')
blogdown::shortcode('tweet', '1222991783933575168')
blogdown::shortcode('tweet', '1222991203110551554')
```
---

Carson Sievert, RStudio  

Reproducible Shiny, Download tab, {shinymeta}  

---
Ellis Hughes, Fred Hutch Cancer Research Center, HIV vaccine  

---
Aymen Waqar  

Building a native iPad dashboard

---
Nathaniel Phillips, Roche  
{FlatironKichen}, a package for a framework for clinical patient data analysis. A data.frame with one row for one patient. It has its unique data.frame and analysis workflow. If once the data.frame is established following analysis becomes easy.  

---

Ana Alyeska Santos, Braulio Cuandon, Biosense Webster, Inc.

Reproducible Engineering Test Reports

---
Ron Keizer, InsightRX  
Medical device with R, InsightRX/PKPDsim  

---
Justin Juskewitch, Mayo Clinic  
Transfusion platelet selection and match for patient and documentation automation  

---
Platelet need and bed occupation prediction and its applications

---
Alicia Schep, Outlier AI

She moved R from Python. {vlBuildr} API develop Altair and Vega-Lite  

---

Tyson Barrett  

List-columns in data.table

data.table can easily convert list-columns

```{r}
blogdown::shortcode('tweet', '1223004598572437504')
```

---
Lionel Hennry, RStudio  
Advances in tidyeval  

History of data masking a.k.a. lazy evaluation
Problem  
* Can not through argument in function, solution {{}}  
* Ambiguity of environment, solution .data and .env
* !! is low level syntax  

---

Lightning Talk

Mexican election prediction

```{r}
blogdown::shortcode('tweet', '1223021112117743618')
```

Rebecca Barter Becoming an R Blogger  

```{r}
blogdown::shortcode('tweet', '1221852227184128000')
```

Other sessions, not check-in  

```{r}
blogdown::shortcodes('tweet', c('1222998335239290880',
                                '1222651913352577024',
                                '1222612815694856193',
                                '1222965028229271558',
                                '1222931681570504704',
                                '1222679720455618560',
                                '1222559524839542784',
                                '1223317400054988801'))
```

@fellgernon kindly tweeted me.

```{r}
blogdown::shortcodes('tweet', user ="fellgernon", id = c('1224034257712173057', '1224561372236828672'))

```

And he left some inspiring post.
http://lcolladotor.github.io/2020/02/03/conference-feelings-from-newbie-to-sponsor/