---
title: "Genotyping diagnosis of gestational trophoblastic disease"
author: 
  - "Jun Kang"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
library(citr)
BibOptions(check.entries = FALSE,
           bib.style = "numeric",
           cite.style = "numeric",
           hyperlink = FALSE,
           dashed = FALSE,
           first.inits = TRUE,
           no.print.fields = c("doi", "url", "isbn", "urldate"))
#myBib <- ReadBib(here::here("static/slide/scarHRD/slides/scarHRD.bib"), check = FALSE)
```
## Terminology

* Digyny: process of a diploid ovum becoming fertilized by a monoploid sperm
* Diandry: fertilization of an egg by two sperm, or by a diploid sperm
* Diandric, monogynic triploid genome: partial hydatidiform mole (PHM)
  + Dispermic/heterogygous PHM
    - Two sperm fertilization
  + Monospermic/hetergozygous PHM
    - One spermatozoon failure of meiosis I or II 
* Digynic triploidy: mimic PHM


